Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:
用户低估来信息接受人数
***

### Scatterplots
Notes:对于连续的变量，要探究其相关性时，散点图是最好的选择

```{r Scatterplots, echo=TRUE}
pf <- read.csv("../lesson3/pseudo_facebook.tsv", sep="\t")
library(ggplot2)
qplot(x=age, y=friend_count, data=pf)
```

```{r Scatterplots1}
ggplot(aes(x=age, y=friend_count), data=pf) +
  geom_point()
```


***

#### What are some things that you notice right away?
Response:
多点过于集中，年龄可能存在虚假报告
***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
ggplot(aes(x=age, y=friend_count), data=pf) +
  geom_point(alpha=0.05) +
  xlim(13,90)
```

***

### Overplotting
Notes:因为点重叠无法真是反应出年龄和朋友数量的关系（因为年龄是连续性书之后），可以使用jitter方法来人为增加noise，以增强显示点。下图就是使用jitter后展现效果

```{r Overplotting}
ggplot(aes(x=age, y=friend_count), data=pf) +
  geom_jitter(alpha=0.05) +
  xlim(13, 90)
```

#### What do you notice in the plot?
Response:在60岁左右的用户的朋友数具有明显的数量多；即使是年轻人朋友数量也主要集中在2000人以下

***

### Coord_trans()
Notes:[coor_trans文档](http://ggplot2.tidyverse.org/reference/coord_trans.html)
is different to scale transformations in that it occurs after statistical transformation and will affect the visual appearance of geoms - there is no guarantee that straight lines will continue to be straight.

示例：
coord_trans(x = "identity", y = "identity", limx = NULL, limy = NULL,
  xtrans, ytrans)


```{r Coord_trans()}
ggplot(aes(x=age, y=friend_count), data=pf) +
  geom_point(alpha=0.05) +
  xlim(13, 90)+
  coord_trans(y="sqrt")
```


#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!
在使用jitter是需要注意，如果直接使用jitter的话，可能因为点在0上使用sqrt之后而出现虚数，为了避免该情况，使用position参数来指定针对age进行抖动。下图是使用position之后的图，可以看出没有出现y轴0以下的数。关于[position_jitter解释](http://ggplot2.tidyverse.org/reference/position_jitter.html)


```{r Coord_trans()_1}
ggplot(aes(x=age, y=friend_count), data=pf) +
  geom_point(alpha=0.05, position=position_jitter(h=0)) +
  xlim(13, 90)+
  coord_trans(y="sqrt")
```


#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
ggplot(aes(x=age, y=friendships_initiated), data=pf) +
  geom_jitter(alpha=0.05) +
  xlim(13, 90)
```

```{r Alpha and Jitter1}
ggplot(aes(x=age, y=friendships_initiated), data=pf) +
  geom_point(alpha=0.05, position=position_jitter(h=0)) +
  coord_trans(y="sqrt")+
  xlim(13, 90)
```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:使用dplyr库，进行相关处理，注意函数n不需要使用参数——它是直接用于结算数量的

```{r Conditional Means}
library(dplyr)
pf.fc_by_age <- pf %>% group_by(age) %>% 
  summarise(mean=mean(friend_count), median=median(friend_count), n=n()) %>% 
  arrange(age)
pf.fc_by_age
```

Create your plot!

```{r Conditional Means Plot}
ggplot(aes(x=age, y=mean), data=pf.fc_by_age) +
  geom_line() +
  scale_x_continuous(limits=c(13,90))
```

***

### Overlaying Summaries with Raw Data
Notes:如果需要在图形上添加摘要信息，可以使用相关的图形，并且加入相关的统计信息参数，如geom_line(stat="summary", fun.y=mean)——其中stat表示统计方法，fun.y针对的是使用统计的函数

```{r Overlaying Summaries with Raw Data, echo=TRUE}
ggplot(aes(age, friend_count), data=pf) +
  coord_cartesian(xlim=c(13,90), ylim=c(0,2000)) +
  geom_point(alpha=0.05, position=position_jitter(h=0), color="orange") +
  coord_trans(y="sqrt") +
  geom_line(stat="summary", fun.y=mean) +
  geom_line(stat="summary", fun.y=quantile, fun.args=list(probs=.1), linetype=2, color="blue") +
  geom_line(stat="summary", fun.y=quantile, fun.args=list(probs=.9), linetype=2, color="blue") +
  geom_line(stat="summary", fun.y=quantile, fun.args=list(probs=.5), color="blue")
```

#### What are some of your observations of the plot?
Response:
年龄越大朋友数量反而会表现增大的趋势，所有的朋友数都集中在1000以下
***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
with(pf, cor(age, friend_count))
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:
with方法的使用是不仅减少了数据输入，而且加快运行速度
```{r Correlation on Subsets}
with(subset(pf, age<=70), cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

```{r different correlation method}
with(subset(pf, age<=70), cor.test(age, friend_count, method="spearman"))
```

## Create Scatterplots
Notes:

```{r}
ggplot(aes(x=www_likes_received, y=likes_received), data=pf) + 
  geom_point(alpha=.05) +
  coord_cartesian(ylim=c(0,10000), xlim=c(0, 6000))
```

***

### Strong Correlations
Notes:

```{r Strong Correlations, echo=TRUE}
ggplot(aes(x=www_likes_received, y=likes_received), data=pf) +
  geom_point() +
  xlim(0, quantile(pf$www_likes_received, .95)) +
  ylim(0, quantile(pf$likes_received, 0.95)) +
  geom_smooth(method="lm", color="red")
```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}
with(pf, cor.test(www_likes_received, likes_received), method="pearson")
```

Response:

***

### Moira on Correlation
Notes:
相关性对于探究多变量之间关系具有重要且直观的意义，可以推动是否需要继续研究两者之间关系。但是需要注意，直接使用相关性探究可能得到的数值是具有强相关性，但是在推荐使用scatter plot来继续查看是否具有某种相关性。 
***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
library(alr3)
```

Create your plot!

```{r Temp vs Month, echo=TRUE}
ggplot(aes(Month, Temp), data=Mitchell) +
 geom_point()
```

```{r cor}
with(Mitchell, cor.test(Month, Temp))
```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}

```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data, echo=TRUE}
ggplot(aes(Month, Temp), data=Mitchell) +
  geom_point() +
  scale_x_continuous(breaks=seq(0, max(Mitchell$Month), 11)) +
  geom_path()
```

***

### A New Perspective

What do you notice?
Response:从时间周期来看，一个人的年龄还可以延伸到多少岁几个月——因为具有时间周期性，所以接下来将使用增加月份来探究


Watch the solution video and check out the Instructor Notes!
Notes:因为年龄里面的线不是平滑的，猜测具有噪点，因此通过对年龄调整来把年龄数据细化在探索

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
pf$age_with_month <- with(pf, age + (1 - dob_month/12))
```

***

### Age with Months Means

```{r Age with Months Means}
pf.fc_by_age_months <- pf %>% 
  group_by(age_with_month) %>% 
  summarise(mean=mean(friend_count), median=median(friend_count), n=n()) %>% 
  arrange(age_with_month)
head(pf.fc_by_age_months)
```

Programming Assignment
```{r Programming Assignment}
ggplot(aes(age_with_month, mean), data=pf.fc_by_age_months) +
  geom_line() +
  xlim(13, 70) +
  ylim(0, 500)
```

***

### Noise in Conditional Means
针对
```{r Noise in Conditional Means}
library(gridExtra)
p1 <- ggplot(aes(x=age, y=mean), data=subset(pf.fc_by_age, age<71)) +
  geom_line() #只探索0-70岁的用户
p2 <- ggplot(aes(age_with_month, mean), data=subset(pf.fc_by_age_months, age_with_month<71)) +
  geom_line() #增加噪点研究年龄上的平均朋友数变化
grid.arrange(p2, p1, ncol=1)
```

***
减小年龄间的范围，参考方法是使用[局部回归思路](https://en.wikipedia.org/wiki/Local_regression)，直观图解见[文档](https://simplystatistics.org/2014/02/13/loess-explained-in-a-gif/)
### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means, echo=TRUE}
library(gridExtra)
p1 <- ggplot(aes(age, mean), data=subset(pf.fc_by_age, age<71)) +
  geom_line() #只探索0-70岁的用户
p2 <- ggplot(aes(age_with_month, mean), data=subset(pf.fc_by_age_months, age_with_month<71)) +
  geom_line() #增加噪点研究年龄上的平均朋友数变化
p3 <- ggplot(aes(round(age/5)*5, friend_count), data=subset(pf, age<71))+
  geom_line(stat="summary", fun.y=mean) #通过更改用户年龄来改变绘图是用到的年龄段，减少noise——将5岁年龄内的数据归为一类
grid.arrange(p2, p1, p3, ncol=1)
```

```{r Smoothing Conditional Means1, echo=TRUE}
library(gridExtra)
p1 <- ggplot(aes(age, mean), data=subset(pf.fc_by_age, age<71)) +
  geom_line() +
  geom_smooth() #只探索0-70岁的用户
p2 <- ggplot(aes(age_with_month, mean), data=subset(pf.fc_by_age_months, age_with_month<71)) +
  geom_line() +
  geom_smooth() #增加噪点研究年龄上的平均朋友数变化
p3 <- ggplot(aes(round(age/5)*5, friend_count), data=subset(pf, age<71))+
  geom_line(stat="summary", fun.y=mean) #通过更改用户年龄来改变绘图是用到的年龄段，减少noise——将5岁年龄内的数据归为一类
grid.arrange(p2, p1, p3, ncol=1)
```

从上图看出，在第二种方案中更容易产生系统误差
***

### Which Plot to Choose?
Notes:
数据折衷是多种方案的选择，不适单独某个方案的能够确定关系。所以数据分析时，最佳方案时选择多个方案进行分析
***

### Analyzing Two Variables
Reflection:散点图，相关系数，模型判断，jitter，多方案折衷

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

