Lesson 3
========================================================

***

### What to Do First?
Notes:

***
```{r list the file in the current directory}
list.files()
```
### Pseudo-Facebook User Data
Notes:了解数据的结构，变量名称及其意义；设定需要分析的目标及内容：1）了解用户；2）了解用户行为

```{r Pseudo-Facebook User Data}
pf <- read.csv("pseudo_facebook.tsv", sep="\t")
print("The structure of the data")
str(pf)
print("The names of the data")
names(pf)
```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays, include=FALSE}
# install.packages('ggplot2')
library(ggplot2)
qplot(x=dob_day, data=pf) +
  scale_x_continuous(breaks=1:31)
```

***

#### What are some things that you notice about this histogram?
Response:
在1号和15号出生的人数最多
***

### Moira's Investigation
Notes:探查实际阅读用户

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:

#### How many of your friends do you think saw that post?
Response:

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:

***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting}
qplot(x=dob_day, data=pf) +
  scale_x_continuous(breaks=1:31) +
  facet_wrap(~dob_month, ncol=3)
```

#### Let’s take another look at our plot. What stands out to you here?
Response:

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:分类：1）极端条件下的坏数据；2）极端条件下的好数据；3）非极端条件下坏数据
#### Which case do you think applies to Moira’s outlier?
Response:极端条件下的坏数据

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?
```{r Friend Count}
qplot(x=friend_count, data=pf, geom="histogram")
```

```{r Friend Count1}
ggplot(aes(x=friend_count), data=pf) +
  geom_histogram()
```

#### How is this plot similar to Moira's first plot?
Response:都是偏态分布
***

### Limiting the Axes
Notes:
```{r Limiting the Axes}
qplot(x=friend_count, data=pf, xlim=c(0,1000), binwidth=25)
```

```{r Limiting the Axes1}
qplot(x=friend_count, data=pf) +
  scale_x_continuous(limits=c(0,1000), breaks=seq(0,1000,50))
```

### Exploring with Bin Width
Notes:
```{r}
ggplot(aes(x=friend_count), data=pf) +
  geom_histogram(binwidth=25) +
  scale_x_continuous(limits=c(0,1000), breaks=seq(0, 1000, 50))
```
***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender, nrow=2)
```

***

### Omitting NA Values
Notes:通过使用subset来筛选数据。当然在使用数据之前可以使用om.rm的参数，但是需要注意该参数会将所有有NA值的数据都删除

```{r Omitting NA Values}
ggplot(aes(x=friend_count), data=subset(pf, !is.na(gender))) +
  geom_histogram(binwidth=25) +
  scale_x_continuous(limits=c(0,1000), breaks=seq(0,1000,50)) +
  facet_wrap(~gender, nrow=2)
```

***


### display the level value

```{r}
table(pf$gender)
```
### Statistics 'by' Gender
Notes:
by(data, INDICES, FUN, ..., simplify = TRUE)
Arguments

data	
an R object, normally a data frame, possibly a matrix.
INDICES	
a factor or a list of factors, each of length nrow(data).
FUN	
a function to be applied to (usually data-frame) subsets of data.
...	
further arguments to FUN.
simplify	
logical: see tapply.

```{r Statistics \'by\' Gender}
by(pf$friend_count, pf$gender, summary)
```

#### Who on average has more friends: men or women?
Response:
female
#### What's the difference between the median friend count for women and men?
Response:
22
#### Why would the median be a better measure than the mean?
Response:
中位数不易受到极值影响
***

### Tenure
Notes:

```{r Tenure}
ggplot(aes(x=tenure), data=pf) +
  geom_histogram(color="black", fill="#099DD9", binwidth=30)
```

***

#### How would you create a histogram of tenure by year?

```{r Tenure1}
ggplot(aes(x=tenure/365), data=pf) +
  geom_histogram(color="black", fill="#099DD9") +
  scale_x_continuous(breaks=seq(1, 7, 1), lim=c(0, 7))
```

***

### Labeling Plots
Notes:条件标签需要使用xlab、ylab

```{r Labeling Plots}
ggplot(aes(x=tenure/365), data=pf) +
  geom_histogram(color="black", fill="orange") +
  scale_x_continuous(limits=c(1,7), breaks=seq(1,7,1)) +
  xlab("The year of tenure")+
  ylab("The frequency")
```

***

### User Ages
Notes:

```{r User Ages}
ggplot(aes(x=age), data=pf) +
  geom_histogram(fill="blue", color="black") 
```

#### What do you notice?
Response:
年龄中有超过100岁的
***

### The Spread of Memes
Notes:
模因一般都和时间具有相关性，
***

### Lada's Money Bag Meme
Notes:
信息热度随着时间进行不同的变化
***

### Transforming Data
Notes:
当数据差异过分大时，可以使用相关方法进行转换。log，sqrt等
***

### Add a Scaling Layer
Notes:
整合图形，可以使用grid.arrange()
```{r Add a Scaling Layer}
library(gridExtra)
p1 <- ggplot(aes(x=friend_count), data=pf) +
  geom_histogram(color="black", fill="blue")+
  xlab("friend count") +
  scale_x_continuous()
p2 <- ggplot(aes(x=friend_count), data=pf) +
  geom_histogram(color="black", fill="blue")+
  xlab("sqrt friend count") +
  scale_x_sqrt()
p3 <- ggplot(aes(x=friend_count), data=pf) +
  geom_histogram(color="black", fill="blue") +
  xlab("log10 friend count") +
  scale_x_log10()
grid.arrange(p1, p2, p3, ncol=1)
```

***


### Frequency Polygons
同样可以使用qplot，需要添加颜色参数和geom图形参数，geom="freqpoly", color=gender

```{r Frequency Polygons}
ggplot(aes(x = friend_count, y = ..count../sum(..count..)), data = subset(pf, !is.na(gender))) + 
  geom_freqpoly(aes(color = gender), binwidth=10) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 100)) + 
  xlab('好友数量') + 
  ylab('Percentage of users with that friend count')
```

```{r Frequency Polygons1}
ggplot(aes(x=www_likes), data=subset(pf, !is.na(gender))) +
  geom_freqpoly(aes(color=gender)) +
  scale_x_log10()
```

***

### Likes on the Web
Notes:
by(data, INDICES, FUN, ..., simplify = TRUE)
女性比男性更喜欢使用网络点赞
```{r Likes on the Web}
by(pf$www_likes, pf$gender, sum)
```


***

### Box Plots
Notes:异常值判断方式：1）通过1.5\*IQR的值来判断， 2）通过3\*sigma的范围来判断。在设置y轴的限制值的时候，使用coord_cartesian(ylim=c(0,1000))的方式，可以避免因为去除了部分值引起的IQR值变化
```{r Box Plots}
ggplot(aes(x=gender), data=subset(pf, !is.na(gender))) +
  geom_boxplot(aes(y=friend_count))
```

```{r Box Plots1}
ggplot(aes(x=gender, y=friend_count), data=subset(pf, !is.na(gender))) +
  geom_boxplot()
```
```{r Box Plots2}
ggplot(aes(x=gender, y=friend_count), data=subset(pf, !is.na(gender))) +
  geom_boxplot() +
  coord_cartesian() +
  ylim(limits=c(0,1000))
```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}
qplot(x=gender, y=friend_count, data=subset(pf, !is.na(gender)), geom="boxplot") +
  coord_cartesian(ylim=c(0,1000))
```

***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}
ggplot(aes(x=gender, y=friendships_initiated), data=subset(pf, !is.na(gender))) +
  geom_boxplot() +
  coord_cartesian(ylim=c(0,700))
```
```{r summary}
by(pf$friendships_initiated, pf$gender, summary)
```

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}
by(pf$friendships_initiated, pf$gender, summary)
```

```{r using mobile}
pf$mobile_check_in <- ifelse(pf$mobile_likes>0, 1, 0)
table(pf$mobile_check_in) / length(pf$mobile_check_in)
```
Response:

***

### Getting Logical
Notes:

```{r Getting Logical}
pf$mobile_check_in <- ifelse(pf$mobile_likes>0, 1, 0)
```

Response:

***

### Analyzing One Variable
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!